Home

### 2019-05-27 analysis/index.Rmd
analysis/timeline.Rmd

Welcome to my research website.

Click on this [link](defoliation-maps.html) to see my results.

>>>>

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/pat-s/2019-feature-selection/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.5.0-brightgreen.svg)](https://cran.r-project.org/) [![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2582969.svg)](https://doi.org/10.5281/zenodo.2582969)

This [workflowr]() site contains all information and results about this research project.

Project details can be found in the [About](about.html) page.

**Result shortcuts**

1. [Prediction maps of defoliation at trees](report-defoliation.html)

Powered by [drake](https://github.com/ropensci/drake) + [workflowr](https://github.com/jdblischak/workflowr) + [mlr](https://github.com/mlr-org/mlr).
